### 2024-09-27 AISTAT25/aistats.tex
cleaning

We begin with a large collection of \emph{balls}, $\B$, of varying
sizes (Fig.~\ref{fig:challenges}(a)). We use label queries to assign
\emph{biases} $\yh(B) \in \{-1,0,+1\}$ to balls $B \in \B$, beginning
with the largest balls. A bias of $+1$ means that the average
$\eta(x)$ in $B$ is significantly positive; bias $-1$ means it is
significantly negative; and bias $0$ means the average $\eta$ is close
to 0. As time goes on, we get biases for progressively smaller balls,
as needed. The final label assigned to any point $x$ is based on the
biases of balls containing just $x$.

@@

These three challenges go beyond earlier work in active learning, which was able to avoid problems like mind-changes by making smoothness assumptions on $\eta$. By tackling all three of them, we are able to give a
universal active learning scheme.

The rest of the paper is organized as follows. Section~\ref{sec:relatedwork} describes related work.
Section~\ref{sec:algorithm} presents the active learning algorithm and Section~\ref{sec:discrete} analyzes it in generality, taking $X$ to be an arbitrary point-set and allowing any $\eta$ function. We identify two \emph{critical levels} for any $x \in X$: two scales (of ball sizes) that control how many queries are sufficient for $x$ to be correctly labeled (Theorem~\ref{thm:label-complexity}). We instantiate these bounds in canonical one-dimensional settings (Theorems~\ref{thm:oned-massart} and \ref{thm:oned-monotonic}) to get label complexities logarithmic in $|X|$.

Section~\ref{sec:continuous} considers the statistical setting where $X$ is drawn from an underlying distribution $\mu$ on $\X$. We give rates of convergence under distributional conditions (Theorem~\ref{thm:label-complexity-specific}), and instantiate them under common assumptions from learning theory and computational geometry.

@@

This work can mostly be grouped by overall principle: either (1) they
seek to obtain the Bayes-optimal labels of a few well-positioned
points, and then propagate these to the rest of the space
\cite{DNZ15,H17,ASU18} or (2) they estimate the biases (positive or
negative) of entire regions at a time \cite{DH08,M12}. In this paper,
we follow the second strategy because the only reliable and
general-purpose way to assess the bias of an individual point,
$\mbox{sign}(\eta(x))$, is to query that point repeatedly; absent
smoothness assumptions, the sign can change abruptly in an arbitrarily
small ball around $x$. On the other hand, the bias of a region
$B$---the sign of the average $\eta$ value in $B$---is easy to
determine given a reasonable number of points from that region.

@@

The two basic entities in our algorithm are the collection of points
$X$ and a collection $\B$ of balls. Sampling is organized around a the
collection $\B$. Balls are the atomic sets on which we assess label
bias.

@@

\begin{figure*}[t]{6in}
\framebox{
\begin{minipage}[t]{6in}
\begin{center}
\vspace{.1in}
\textbf{Repeat for $\ell=0,1,2,\ldots,\log |X|-1$:}
\begin{enumerate}[leftmargin=0.6cm]
\item \label{step:Uell} {\bf Compute uncertainty set:}\\ If $\ell=0$, set $U_0 = X$; otherwise set $U_\ell = \{x \in X: \yh_{\ell-1}(x) = \,!, \ \yh_\ell(x) = \bot\}$t
\item \label{step:QS} {\bf Compute Focused Query set:}\\ Compute query ball set be $R=  \bigcup_{x \in U} \B_\ell(x)$
and focused query set $S=\bigcup_{B \in R} B$
\item \label{step:sample} {\bf Make queries:}\\
\textbf{Repeat until} number of queries in each ball $B \in R$ is at least $C/\gamma^2$
  \begin{enumerate}[leftmargin=0.6cm]
  \item Select a {\tt query} uniformly at random from $S$
  \end{enumerate}

@@

\subsection{Simplified algorithm}

We now describe the simplified algorithm here referred to simply as
the algorithm. The algorithm loops over increasing levels.  At each
level it identifies the set of ``known unknowns'' which approximates
the boundary. The algorithm then makes queries in the vicinity of the
boundary to refine it and proceeds to the next finer level.

What follows is a detailed explanation of  Figure~\ref{alg:simple}.

The outer loop of the algorithm iterates over the
levels, starting with $\ell=0$ that corresponds to balls that contain
at least half of the points in $X$, and ending with $\ell=\log |X|-1$,
corresponding to balls that contain a single point.

The loop consists of five steps. The first computes the uncertainty set, the second computes the focused query
set, the third defines the sampling process, the fourth and fifth
update the labels of the balls and the points respectively.

@@

In step~\ref{step:QS} the algorithm identifies the balls that needs to
be queried in order to get more information about $U_\ell$. These are
the balls in $\B_l$ that contain at least one point of $U_\ell$.  The
set $S$ is the union of these balls and defines the ``focus area''
which is queried in order to reduce the known unknowns.

In step~\ref{step:sample} the algorithm queries points inside the
focus area repeatedly at random.  This step terminates once there are
$C/\gamma^2$ samples in each of the balls in the focus area.

Step ~\ref{step:balls} associates a label with each ball. The
label is one of $\{-1,+1,0\}$.  The labels $+1$ and $-1$ correspond to
a confident statement that $\eta(B)>0$ and $\eta(B)<0$
respectively. Finally, the label $0$ indicates that the sign of $B$
is uncertain given the answers to the queries.

In step~\ref{step:examples} these labels are propagated to the
examples.  This is done in two sub-steps. First the {\em Possible
  Labels} for $x$ denoted $\PL_\ell(x)$ are calculated. $\PL_\ell(x)$
contains $+1$ if there is a ball containing $x$ whose label is $+1$,
symmetrically for $-1$. The label $\yh_\ell(x)$ is determined by the
possible labels set $\PL_\ell(x)$ as described in
step~\ref{step:examples}. The most significant label is ``!'', which
indicates balls with conflicting polarity containing $x$. Points
labeled ``!'' determine the uncertainty region and the focused query
region in the following level and the process repeats.

@@

  A related problem is that having the outer loop iterate over levels
  will cause the algorithm to miss some uncertainty region if they are
  appear at a lower level. Therefor the full algorithm does not loop
  over levels. Instead, at each iteration it finds the lowest level
  where the uncertainty set is not empty and makes two queries, one
  focused and one background.

@@

The querying process can be stopped at any time, whereupon labels are assigned as follows:
\begin{equation}
\yh(x) = 
\left\{
\begin{array}{cl}
  \yh_\ell(x) & \mbox{largest $\ell$ with $\yh_\ell(x) \in \{-1,+1\}$,1}\\
  & \mbox{if such an $\ell$ exists} \\
0 & \mbox{``don't know'', otherwise}
\end{array}
\right.
\label{eq:final-label}
\end{equation}

@@

\begin{itemize}[leftmargin=0.5cm]
\item Define querying region:
$$ S =  \bigcup_{x \in U} \bigcup_{B \in \B_\ell(x)} \{z \in X_B: T_z \leq \tau_\ell\} $$
\item Query the next unlabeled point in $S \setminus Q$, ordered by increasing $T_x$ values, and add to $Q$
\end{itemize}

@@

\pagebreak
In the next definition and lemma we establish that the bias estimates for all balls in $\B$ are sufficiently accurate. 
\begin{defn}
\label{def:accurate-bias-estimate}
For any $B \in \B$, bias estimate $\yh(B) \in \{+1,-1,0\}$ is \emph{$\gamma$-accurate} if:
\begin{itemize}
\item $\yh(B) = +1 \implies \eta_X(B) > 0$
\item $\yh(B) = -1 \implies \eta_X(B) < 0$
\item $\yh(B) = 0 \implies |\eta_X(B)| < \gamma$
\end{itemize}
\end{defn}

@@

A common intuition about active learning is that successive queries gradually constrain the possible locations of the decision boundary. Let's consider the state of affairs when all balls at level $\leq \ell - 1$ have been sampled. The known-unknowns from this level are points $x$ with $\yh_{\ell-1}(x) = \, !$; by Lemma~\ref{lemma:boundary}(b), such points must have $L_2(x) \geq \ell$. Focused sampling at level $\ell$ is restricted to balls that contain these points. We will think of this region as the \emph{boundary set} at level $\ell$.
\begin{defn}[Boundary set $\bf \Delta_\ell$]
For any level $\ell$, define the \emph{boundary set} at level $\ell$ to be
\begin{equation}
\Delta_\ell 
= \bigcup_{x \in X: L_2(x) \geq \ell} \bigcup_{B \in \B_{\ell}(x)} X_B 
.
\label{eq:sampling-region}
\end{equation}
\end{defn}
%It can be shown that all focused samples at level $\ell$ must lie in this set.
\begin{lemma}
All focused samples at level $\ell$ lie in $\{z \in \Delta_\ell: T_z \leq \tau_\ell \}$.
\label{lemma:focused}
\end{lemma}

@@

To apply Theorem~\ref{thm:label-complexity}, we need bounds on the critical levels $L_1(x)$ and $L_2(x)$ for each $x \in X$, and on the size of the sampling region $\Delta_\ell$ at each level $\ell$. We now derive these in some canonical settings.

@@

A counting argument then shows that the boundary region shrinks exponentially as the level increases, $|\Delta_\ell| \leq 4n/2^\ell$, yielding the following label complexity. 
\begin{thm}
Define $r^+ = \min \{r(x): x \in X \cap [\lambda_R,1]\}$ and $r^- = \min \{r(x): x \in X \cap [0,\lambda_L]\}$. Pick any $0 < \delta < 1$. Suppose we run the algorithm of Fig.~\ref{alg:main} with $k = O((\log (n/\delta))/\gamma^2)$ and that $\min(r^+, r^-) \geq 2k$.  Take any 
$$ m \geq 64k \cdot \max \left( \frac{n}{\min(n^+,n^-)}, \ 2 \lg \frac{\min(n^+,n^-)}{\min(r^+,r^-)} \right) .$$
With probability $\geq 1-\delta$, after $m$ queries the algorithm correctly labels all $x \in X$ with $|\eta(x)| \geq \gamma$.
\label{thm:oned-monotonic}
\end{thm}
If $n^+, n^- = \Theta(n)$, that is, a constant fraction of the points lie to the left of $\lambda_L$ and to the right of $\lambda_R$, then the label complexity is $O(\log^2 n)$. If in addition $r^+, r^- = \Theta(n)$, that is, a constant fraction of the points lie between $\lambda_L, \lambda_R$ and the decision boundary, the label complexity is $O(\log n)$.

@@

\section{Experiments}

We describe an experiment designed to evaluate our algorithm.
We use a simple 1D problem, described in Section~\ref{sec:example-massart}.
Although this problem is simple, it is outside the scope of most non-parametric active learning algorithms, which assume smoothness of the conditional probability.

@@

 For our experiment we used a sample of 10,000 unlabeled points, we repeated each of our experiments 20 times. In Figure~\ref{fig:Experiments} we show the average performance of these experiments. Note the horizontal line segments marked "active vs. passive ... ", these compare the number of queries required by the active and the passive algorithms for different accuracies
 These numbers are repeated in the following table.
\begin{tabular}{|c|rr|}
\hline
err-opt &  Active&  Passive \\
\hline
0.02  &    320 &     517 \\
0.01 &     429 &    1035 \\
0.005 &678 &    2045 \\
\hline
\end{tabular}
Considering the columns for the Active and Passive algorithms respectively, we see that the experimental query complexities concur with the theoretical predictions.

\section{Future Directions}
Our algorithm is generic, while we used euclidean balls for clarity,
any sets can be used. While this generality is attractive, it leaves
open the question of what are good ways to define the collection of
regions. Another aspect of this generality is that the computational
complexity of the algorithm is high. Future work will be directed
towards characterizing region sets that give both high query
efficiency and low computational complexity.

@@

%%%%%%%%%%%%
\section{Analysis Details: Discrete setting}

\subsection{Technicalities: discrete setting}

\subsubsection{Large deviation bounds for the discrete setting}

@@

Let $\overline{U}_\ell$ denote the set of all points that are ever (in any round of sampling) in the uncertainty set at level $\ell$. From Lemma~\ref{lemma:boundary}(b), we see that any $x$ with $L_2(x) < \ell$ has $\yh_{\ell-1}(x) \neq \ !$ and thus never makes it into the uncertainty set at level $\ell$. In short,
\begin{equation}
\overline{U}_{\ell} \subset \{x \in X: L_2(x) \geq \ell\}.
\label{eq:uncertainty}
\end{equation}

@@

{\it Case 1:} Fewer than $m/4$ focused queries are made in phase two. This can only happen if some round of sampling has an empty uncertainty set, meaning that all of $A$ has left $U$ at that point.

>>>>

We begin with a large collection of \emph{balls}, $\B$, of varying
sizes (Fig.~\ref{fig:challenges}(a)). We use label queries to assign
\emph{biases} $\yh(B) \in \{-1,0,+1\}$ to balls $B \in \B$, beginning
with the largest balls. A bias of $+1$ means that the average of 
$\eta(x)$ over $s \in B$ is significantly positive; bias $-1$ means it is
significantly negative; and bias $0$ means the average $\eta$ is close
to 0. As time goes on, we get biases for progressively smaller balls,
as needed. The final label assigned to any point $x$ is based on the
biases of balls containing just $x$.

@@

These three challenges go beyond earlier work in active learning,
which was able to avoid problems like mind-changes by making
smoothness assumptions on $\eta$. By tackling all three of them, we
are able to give a universal active learning scheme. Our focus is on
the query complexity of the algorithm, largely ignoring the
computational complexity. However, we do provide some experimental results that demonstrate that the algorithm works on a toy example.

The rest of the paper is organized as
follows. Section~\ref{sec:relatedwork} describes related work.
Section~\ref{sec:algorithm} presents the active learning algorithm and
Section~\ref{sec:discrete} analyzes it in the finite population
setting, taking $X$ to be an arbitrary point-set and allowing any
$\eta$ function. We identify two \emph{critical levels} for any
$x \in X$: two scales (of ball sizes) that control how many queries
are sufficient for $x$ to be correctly labeled
(Theorem~\ref{thm:label-complexity}). We instantiate these bounds in
canonical one-dimensional settings (Theorems~\ref{thm:oned-massart}
and \ref{thm:oned-monotonic}) to get label complexities logarithmic in
$|X|$. In section~\ref{sec:experiment} we describe an experiment that supports the theoretical bound given in Theorems~\ref{thm:oned-massart}.

The supplementary material in
Section~\ref{sec:FinitePopulationProofs}, which contains the proofs of
the theorems from Section~\ref{sec:discrete}.  Finally,
Section~\ref{sec:continuous} considers the statistical setting where
$X$ is drawn from an underlying distribution $\mu$ on $\X$. We give
rates of convergence under distributional conditions
(Theorem~\ref{thm:label-complexity-specific}), and instantiate them
under common assumptions from learning theory and computational
geometry.

@@

This work can mostly be grouped by overall principle: either (1) they
seek to obtain the Bayes-optimal labels of a few well-positioned
points, and then propagate these to the rest of the space
\cite{DNZ15,H17,ASU18} or (2) they estimate the biases (positive or
negative) of entire regions at a time \cite{DH08,M12}. In this paper,
we follow the second strategy because the only reliable and
general-purpose way to assess the bias of an individual point,
$\mbox{sign}(\eta(x))$, is to query that point repeatedly; absent
smoothness assumptions, the sign can change abruptly in an arbitrarily
small ball around $x$. On the other hand, the bias of a region
$B$---the sign of the average $\eta$ value in $B$---is easy to
determine given a reasonable number of queries chosen at random from that region.

@@

The two basic entities in our algorithm are the collection of points
$X$ and a collection of balls $\B$. Sampling is organized around a the
collection $\B$. Balls are the atomic sets on which we assess label
bias.

@@

\begin{figure*}[t]{6in}
\framebox{
\begin{minipage}[t]{6in}
\begin{center}
\vspace{.1in}
\textbf{Repeat for $\ell=0,1,2,\ldots,\log |X|-1$:}
\begin{enumerate}[leftmargin=0.6cm]
\item \label{step:Uell} {\bf Compute uncertainty region:}\\ If $\ell=0$, set $U_0 = X$; otherwise set $U_\ell = \{x \in X: \yh_{\ell-1}(x) = \,!, \ \yh_\ell(x) = \bot\}$t
\item \label{step:QS} {\bf Compute Focused Query region:}\\ Compute query region be $R=  \bigcup_{x \in U} \B_\ell(x)$
and focused query region $S=\bigcup_{B \in R} B$
\item \label{step:sample} {\bf Make queries:}\\
\textbf{Repeat until} number of queries in each ball $B \in R$ is at least $C/\gamma^2$
  \begin{enumerate}[leftmargin=0.6cm]
  \item Select a {\tt query} uniformly at random from $S$
  \end{enumerate}

@@

\subsection{The simplified algorithm}

We now describe the simplified algorithm here referred to simply as
the algorithm. The algorithm loops over increasing levels.  At each
level it identifies the region of ``known unknowns'' which approximates
the boundary. The algorithm then makes queries in the vicinity of the
boundary to refine it and proceeds to the next finer level.

What follows is a detailed explanation of  Figure~\ref{alg:simple}.
The outer loop of the algorithm iterates over the
levels, starting with $\ell=0$ that corresponds to balls that contain
at least half of the points in $X$, and ending with $\ell=\log |X|-1$,
corresponding to balls that contain a single point. Initially, all balls are labeled $\bot$, which indicates that there are not enough queries inside the ball to determine it's label.

The loop consists of five steps. The first computes the {\em uncertainty
region}, the second computes the {\em focused query region}, the third defines the
sampling process, the fourth and fifth update the labels of the balls
and the points respectively.

@@

In step~\ref{step:QS} the algorithm identifies the balls that needs to
be queried in order to get more information about $U_\ell$. These are
the balls in $\B_l$ that contain at least one point of $U_\ell$.  The
region $S$ is the union of these balls and defines the set
from which queries are selected in order to reduce the known unknowns.

In step~\ref{step:sample} the algorithm queries points inside the
focus region repeatedly at random.  This step terminates once there are
$C/\gamma^2$ samples in each of the balls in the focus region.

Step ~\ref{step:balls} associates a label with each ball in the focus region. The
label is one of $\{-1,+1,0\}$.  The labels $+1$ and $-1$ correspond to
a confident statement that $\eta(B)>0$ and $\eta(B)<0$
respectively. Finally, the label $0$ indicates that the sign of $B$
is uncertain given the answers to the queries.

In step~\ref{step:examples} these labels are propagated to the
examples.  This is done in two sub-steps. First the {\em Possible
  Labels} for $x$ denoted $\PL_\ell(x)$ are calculated. $\PL_\ell(x)$
contains $+1$ if there is a ball containing $x$ whose label is $+1$,
symmetrically for $-1$. The label $\yh_\ell(x)$ is determined by the
possible labels set $\PL_\ell(x)$ as described in
Equation~\ref{eq:provisional-label}. The most significant label is ``!'', which
indicates balls with conflicting polarity containing $x$. Points
labeled ``!'' determine the uncertainty region and the focused query
region in the following level and the process repeats.

@@

  A related problem is that having the outer loop iterate over levels
  will cause the algorithm to miss some uncertainty region if they are
  appear at a lower level. Therefor the full algorithm does not loop
  over levels. Instead, at each iteration it finds the lowest level
  where the uncertainty region is not empty and makes two queries, one
  focused and one background.

@@

The querying process can be stopped at any time, whereupon labels are assigned as follows:
\begin{equation}
\yh(x) = 
\left\{
\begin{array}{cl}
  \yh_\ell(x) & \mbox{largest $\ell$ with $\yh_\ell(x) \in \{-1,+1\}$}\\
  & \mbox{if such an $\ell$ exists} \\
0 & \mbox{``don't know'', otherwise}
\end{array}
\right.
\label{eq:final-label}
\end{equation}

@@

\begin{itemize}[leftmargin=0.5cm]
\item Define focus region:
$$ S =  \bigcup_{x \in U} \bigcup_{B \in \B_\ell(x)} \{z \in X_B: T_z \leq \tau_\ell\} $$
\item Query the next unlabeled point in $S \setminus Q$, ordered by increasing $T_x$ values, and add to $Q$
\end{itemize}

@@

In the next definition and lemma we establish that the bias estimates for all balls in $\B$ are sufficiently accurate. 
\begin{defn}
\label{def:accurate-bias-estimate}
For any $B \in \B$, bias estimate $\yh(B) \in \{+1,-1,0\}$ is \emph{$\gamma$-accurate} if:
\begin{itemize}
\item $\yh(B) = +1 \implies \eta_X(B) > 0$
\item $\yh(B) = -1 \implies \eta_X(B) < 0$
\item $\yh(B) = 0 \implies |\eta_X(B)| < \gamma$
\end{itemize}
\end{defn}

@@

A common intuition about active learning is that successive queries gradually constrain the possible locations of the decision boundary. Let's consider the state of affairs when all balls at level $\leq \ell - 1$ have been sampled. The known-unknowns from this level are points $x$ with $\yh_{\ell-1}(x) = \, !$; by Lemma~\ref{lemma:boundary}(b), such points must have $L_2(x) \geq \ell$. Focused sampling at level $\ell$ is restricted to balls that contain these points. We will think of this set as the \emph{boundary set} at level $\ell$.
\begin{defn}[Boundary set $\bf \Delta_\ell$]
For any level $\ell$, define the \emph{boundary set} at level $\ell$ to be
\begin{equation}
\Delta_\ell 
= \bigcup_{x \in X: L_2(x) \geq \ell} \bigcup_{B \in \B_{\ell}(x)} X_B 
.
\label{eq:sampling-region}
\end{equation}
\end{defn}
%It can be shown that all focused samples at level $\ell$ must lie in this set.
\begin{lemma}
All focused samples at level $\ell$ lie in $\{z \in \Delta_\ell: T_z \leq \tau_\ell \}$.
\label{lemma:focused}
\end{lemma}

@@

To apply Theorem~\ref{thm:label-complexity}, we need bounds on the critical levels $L_1(x)$ and $L_2(x)$ for each $x \in X$, and on the size of the sampling set $\Delta_\ell$ at each level $\ell$. We now derive these in some canonical settings.

@@

A counting argument then shows that the boundary set shrinks exponentially as the level increases, $|\Delta_\ell| \leq 4n/2^\ell$, yielding the following label complexity. 
\begin{thm}
Define $r^+ = \min \{r(x): x \in X \cap [\lambda_R,1]\}$ and $r^- = \min \{r(x): x \in X \cap [0,\lambda_L]\}$. Pick any $0 < \delta < 1$. Suppose we run the algorithm of Fig.~\ref{alg:main} with $k = O((\log (n/\delta))/\gamma^2)$ and that $\min(r^+, r^-) \geq 2k$.  Take any 
$$ m \geq 64k \cdot \max \left( \frac{n}{\min(n^+,n^-)}, \ 2 \lg \frac{\min(n^+,n^-)}{\min(r^+,r^-)} \right) .$$
With probability $\geq 1-\delta$, after $m$ queries the algorithm correctly labels all $x \in X$ with $|\eta(x)| \geq \gamma$.
\label{thm:oned-monotonic}
\end{thm}
If $n^+, n^- = \Theta(n)$, that is, a constant fraction of the points lie to the left of $\lambda_L$ and to the right of $\lambda_R$, then the label complexity is $O(\log^2 n)$. If in addition $r^+, r^- = \Theta(n)$, that is, a constant fraction of the points lie between $\lambda_L, \lambda_R$ and the decision boundary, the label complexity is $O(\log n)$.

@@

\section{Experiments}
\label{sec:experiment}
We describe an experiment designed to evaluate our algorithm.
We use a simple 1D problem, described in Section~\ref{sec:example-massart}.
Although this problem is simple, it is outside the scope of most non-parametric active learning algorithms, which assume smoothness of the conditional probability.

@@

 For our experiment we used a sample of 10,000 unlabeled points, we repeated each of our experiments 20 times. In Figure~\ref{fig:Experiments} we show the average performance of these experiments. Note the horizontal line segments marked "active vs. passive <error>", these compare the number of queries required by the active and the passive algorithms for different accuracies
 These numbers are repeated in the following table.
\begin{center}
\begin{tabular}{|c|rr|}
\hline
err-opt &  Active&  Passive \\
\hline
0.02  &    320 &     517 \\
0.01 &     429 &    1035 \\
0.005 &678 &    2045 \\
\hline
\end{tabular}
\end{center}

Considering the columns for the Active and Passive algorithms respectively, we see that the experimental query complexities concur with the theoretical predictions.

\section{Future Directions}
Our algorithm is generic, while we used euclidean balls for clarity,
any sets can be used. While this generality is attractive, it leaves
open the question of what are good ways to define the collection of
regions. Another aspect of this generality is that the computational
complexity of the algorithm is high. Future work will be directed
towards characterizing collections of regions that give both low query
complexity and low computational complexity.

@@

%%%%%%%%%%%%
\section{Analysis Details: Finite Population setting}
\label{sec:FinitePopulationProofs}

\subsection{Technicalities: finite population setting}

\subsubsection{Large deviation bounds for the finite population setting}

@@

Let $\overline{U}_\ell$ denote the set of all points that are ever (in any round of sampling) in the uncertainty region at level $\ell$. From Lemma~\ref{lemma:boundary}(b), we see that any $x$ with $L_2(x) < \ell$ has $\yh_{\ell-1}(x) \neq \ !$ and thus never makes it into the uncertainty region at level $\ell$. In short,
\begin{equation}
\overline{U}_{\ell} \subset \{x \in X: L_2(x) \geq \ell\}.
\label{eq:uncertainty}
\end{equation}

@@

{\it Case 1:} Fewer than $m/4$ focused queries are made in phase two. This can only happen if some round of sampling has an empty uncertainty region, meaning that all of $A$ has left $U$ at that point.
